% !TEX program = xelatex

\usepackage{hyperref}

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yuchen Wang}

\basicInfo{
  \email{wyc8094@gmail.com} \textperiodcentered\ 
	\phone{(+886) 0937069018} \textperiodcentered\ 
	}

\datedsubsection{\textbf{National Taiwan University}, Taipei, Taiwan}{September 2019 -- Now}
\textit{Master} in Computer Science, GPA: 4.23/4.3

\datedsubsection{\textbf{Jinan University}, Guangzhou, China}{September 2014 -- June 2018}
\textit{B.S.} in Computer Science, GPA: 3.68/5.0

\section{\faUsers\ Projects}

\datedsubsection{\textbf{BubbleScript}}{November - December 2019}
\role{Javascript}{Individual Project}
Brief introduction: Real-time bubble simulation based on WebGL and WebVR.
\begin{itemize}
    \item Investigate fluid simulation algorithms on Siggraph 2007 course notes.
    \item Implement shallow water simulation and bubble simulation from paper on SCA 2007.
    \item Adopt whole experience into WebVR.
    \item Demo is at \url{https://aaron19960821.github.io/BubbleScript/}
\end{itemize}

\datedsubsection{\textbf{NoriPlus}}{September 2019 - now}
\role{C++}{Individual Project}
Brief introduction: A simple C++ renderer based on \textbf{Nori}.
\begin{itemize}
    \item Understanding and implement different algorithms in Ray tracing.
    \item Investigate different BRDF models in computer graphics.
    \item Investigate different light transportation methods in computer graphics.
\end{itemize}

\datedsubsection{\textbf{ButterflyDetection}}{March - May 2018}
\role{C++, C}{Individual Project}
Brief introduction: A butterfly detection and classify model based on YOLO and R-CNN.
\begin{itemize}
	\item Investigate the usage of some basic layers(Convolution layer, Max-Pooling layer) in Darknet and change them for proper use.
  \item Implement YOLO-V2 with Darknet.
	\item Apply ResNet50 to improve image classification precision.
\end{itemize}

\datedsubsection{\textbf{Model As A Feature}}{July - October 2017}
\role{C++, C\#}{A Feature in Microsoft Cortana}
Brief introduction: LU model reuse
\begin{itemize}
	\item Investgate the usage of machine learning in LU.
  \item Reuse LU models by linking the output of a model to the input of another model
	\item Optimize Data Storage with Trie Tree.
  \item Optimized NGram and Lexicon feature extractor by 50\%
\end{itemize}

\datedsubsection{\textbf{TinyPainter}}{April - May 2017}
\role{C\#}{Individual Projects}
Brief introduction: A tiny, fast painter in windows implemented by .NET framework.
\begin{itemize}
  \item Implemented a simple painter with basic paint items.
  \item Optimized memory and efficiency with double buffering technique by 40\%
\end{itemize}

\section{\faUsers\ Experience}

\datedsubsection{\textbf{Microsoft}}{July 2018 - September 2019}
\role{Software Engineer}{Manager: Yet Huynh}
Work as a software engineer in Microsoft Edge Team.
\begin{itemize}
    \item Responsible for Extension framework on Edge Android, make Microsoft Edge one of 3 browsers in the world that supports chromium extension on Android.
    \item Work on file downloading for managed account for enterprise feature.
    \item Invesigate and fix Edge Accessibility Feature on Edge Android.
    \item Optimize the reading list feature on Edge Android.
\end{itemize}

\datedsubsection{\textbf{Microsoft}}{July - October 2017}
\role{Software Engineer Intern}{Manager: Yang Yang}
Work as an intern in Microsoft Cortana Team.
\begin{itemize}
    \item Investigate the usage of different ML algorithms in Languages understanding.
    \item Boost up the storage and computing of Cortana cloud platform.
    \item Build a small toolkit to reuse different LU Models.
\end{itemize}

\section{\faCogs\ Publications}
\datedsubsection{\textbf{Find Butterflies in Your Photos}}{2018}
My graduate thesis in Jinan University, was written in Chinese.

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C\# == C++ > Python > > Java
  \item Platform: Linux, MacOS
  \item Development: Back End, Machine Learning
  \item Machine Learning Frameworks: Tensorflow
  \item Computer Graphics: OpenGL, WebGL, Vulkan
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{Silver Prize}, 2017 Guangdong Collage Programming Contest}{May. 2017}
\datedline{\textit{Bronze Prize}, 2016 ACM/ICPC Asia Reginal Qingdao}{November 2016}
\datedline{\textit{Prize}, 2016 JNU Outstanding Student Scolarship}{November 2016}
\datedline{\textit{Prize}, 2015 JNU Outstanding Student Scolarship}{November 2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://aaron19960821.github.io
  \item GitHub: https://github.com/aaron19960821
  \item Languages: English - Fluent 102 in Toefl IBT, Mandarin - Native speaker
\end{itemize}
\end{document}
